---
title: "Ecomm data, amazon"
output: html_document
---
Research question:
Is the average conversion rate significantly different among customers reached through various marketing channelseg Email, social media, paid ads


```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
```
```{r}
df=digital_marketing_campaign_dataset_csv
```
```{r}
sum(duplicated(df))
```
```{r}
summary(df)
```
#checking for missing values per colomn
```{r}
colSums(is.na(df))
```
#Dropping missing values
```{r}
df=na.omit(df)
```

#convert categorical cols to factor
```{r}
df$CampaignChannel= as.factor(df$CampaignChannel)
df$Gender= as.factor(df$Gender)
```
#ensure  numeric cols are numeric
```{r}
df$ConversionRate= as.numeric(df$ConversionRate)
df$Age= as.numeric(df$Age)
df$Income= as.numeric(df$Income)
df$ClickThroughRate= as.numeric(df$ClickThroughRate)
df$AdSpend= as.numeric(df$AdSpend)
```
#run a one way anova
```{r}
model= aov(ConversionRate ~ CampaignChannel,data= df)
summary(model)
```
#visiualise conversion area
```{r}
ggplot(df, aes(x= CampaignChannel, y= ConversionRate))+
   geom_boxplot(fill= "darkgreen")+
  labs(title = "Conversion rate by marketing channel", y= "conversion rate", x="Campaign channel")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
ggplot(df, aes(sample = ConversionRate))+
  stat_qq()+stat_qq_line()+
  facet_wrap(~CampaignChannel, scales= "free")

```
```{r}
library(car)
#install car
leveneTest(ConversionRate ~CampaignChannel, data= df)
```
#Games Howell post hoc test

```{r}
library(rstatix)
library(ggpubr)

games_result = df %>%
  games_howell_test(ConversionRate~ CampaignChannel)
print(games_result)
```



